\begin{enumerate}[label=(\alph*)]
	\item Consider two points $\mathbf{x,y} \in \mathbb{R}^2$ where $\mathbf{x}$ is
	      obtained by rotating $\mathbf{y}$ by counterclockwise by $45^{\circ}$.
	      Can you find a matrix $\mathbf{A}$ such that $\mathbf{x} = \mathbf{A}
		      \mathbf{y}$? Does the matrix depend on the choice of $\mathbf{y}$
	      or $\mathbf{x}$?
	      \begin{tcolorbox}
		      \textbf{Solution:} \par
		      Let
		      $$
			      \mathbf{A} = \begin{bmatrix}
				      \cos 45^{\circ} & -\sin 45^{\circ} \\
				      \sin 45^{\circ} & \cos 45^{\circ}\end{bmatrix}
		      $$
		      This matrix rotates a point in $\mathbb{R}^2$ by $45^{\circ}$
		      counterclockwise. Regardless of the choice of $\mathbf{x}$
		      or $\mathbf{y}$, the matrix $\mathbf{A}$ will always rotate
		      the point $45^{\circ}$ counterclockwise.	      \end{tcolorbox}
	\item Consider the line in $\mathbb{R}^2$ that passes through origin and the
	      point $\left[ 2, -3 \right]^T$. Consider any point $\mathbf{x} \in
		      \mathbb{R}^2$ and let $\mathbf{z}$ be the point on this line which is
	      closest to $\mathbf{x}$ (you can choose your own notion of distance in
	      $\mathbb{R}^2$ as long as you are able to answer the question). Can you
	      find a matrix $\mathbf{B}$ such that $\mathbf{z} = \mathbf{Bx}$? Does
	      $\mathbf{B}$ depend on $\mathbf{x}$?
	      \begin{tcolorbox}
		      \textbf{Solution:} \par
		      We know that $\mathbf{z}$ is the projection of $\mathbf{x}$ onto the line
		      that passes through the origin and $\left[ 2, -3 \right]^T$. Thus,
		      everyone point $\mathbf{z}$ is some scalar multiple of $\left[ 2, -3
				      \right]^T$. Therefore, the vector $\mathbf{z}$ is a
		      multiple of $\mathbf{y}$. Thus, we can write:
		      $$
			      \mathbf{z} = c \mathbf{y}
		      $$
		      Where $c$ is some scalar and $\mathbf{y}$ is the vector that
		      defines the line. Now we want to find a unique value for $c$ for
		      each input $\mathbf{x} \in \mathbb{R}^2$ that we are mapping onto
		      $\mathbf{z}$. We can do this with the following equation:
		      \[
			      \frac{ \langle \mathbf{x}, \mathbf{y} \rangle}{ || \mathbf{y}
				      ||_2^2}
		      \]
		      Here, the dot product of $\mathbf{x}$ and $\mathbf{y}$ is a
		      measure of how similar the $\mathbf{x}$ is to $\mathbf{y}$.
		      The more similar they
		      are, the larger the inner product will be. The more different they
		      are, the smaller the inner product will be. However, since the
		      similarity of the two vectors is relative to the magnitude of
		      $\mathbf{y}$, we divide by the magnitude of $\mathbf{y}$ to
		      normalize the value. Thus, we
		      can plug in the values of $\mathbf{y}$ to get:
		      $$
			      \begin{aligned}
				      \mathbf{z} & = \frac{\mathbf{x} \cdot \left[ 2, -3
						      \right]^T}{|| \left[ 2, -3 \right]^T ||_2^2} \cdot
				      \left[ 2, -3 \right]^T                                   \\
				                 & = \frac{2x_1 - 3x_2}{13} \cdot \left[ 2, -3
					      \right]^T
			      \end{aligned}
		      $$
		      We can convert this to matrix form:
		      $$
			      \mathbf{z} =
			      \begin{bmatrix}
				      \frac{4}{13}  & -\frac{6}{13} \\
				      -\frac{6}{13} & \frac{9}{13}
			      \end{bmatrix}
			      \mathbf{x}, \quad
			      \mathbf{B} =
			      \begin{bmatrix}
				      \frac{4}{13}  & -\frac{6}{13} \\
				      -\frac{6}{13} & \frac{9}{13}
			      \end{bmatrix}
		      $$
		      Here, $\mathbf{B}$ does not depend on the vector $\mathbf{x}$ that
		      you want to project onto the line, but does depend on the vector
		      $\mathbf{y}$ that defines the line.
	      \end{tcolorbox}
\end{enumerate}
